---
title: "`r read.dcf('DESCRIPTION', fields = 'Package')[1]`"  
author: "`r rworkflows::use_badges()`" 
date: "<h4>README updated: <i>`r format( Sys.Date(), '%b-%d-%Y')`</i></h4>"
output:
  github_document
---

<!-- To modify Package/Title/Description/Authors fields, edit the DESCRIPTION file -->

```{r, echo=FALSE, include=FALSE}
pkg <- read.dcf("DESCRIPTION", fields = "Package")[1]
title <- gsub("\n"," ",read.dcf("DESCRIPTION", fields = "Title")[1])
description <- gsub("\n"," ",read.dcf("DESCRIPTION", fields = "Description")[1])
URL <- read.dcf('DESCRIPTION', fields = 'URL')[1]
owner <- strsplit(URL,"/")[[1]][4]
repo <- strsplit(URL,"/")[[1]][5]
```
 
**\<---⬇️⬇️⬇️(Start of section that can be deleted after forking the template)⬇️⬇️⬇️---\>** 

## Citation

If you use the `templateR` R package template, 
or any of the [`rworkflows`](https://github.com/neurogenomics/rworkflows) suite tools,
please cite:

> Brian M. Schilder, Alan E. Murphy, & Nathan G. Skene (2023) The rworkflows suite: automated continuous integration for quality checking, documentation website creation, and containerised deployment of R packages, Research Square; https://doi.org/10.21203/rs.3.rs-2399015/v1

## Setup

`templateR` is a template designed to make developing new R packages easy by providing:  

  - **DESCRIPTION, vignettes/, tests/, R/, man/, inst/**: Basic skeleton for the package itself.  
  - **README.Rmd**: Auto-populates based on the *DESCRIPTION* file (that can be knit to create *README.md*). Also contains [badges](https://github.com/GuangchuangYu/badger) that automatically update themselves.   
  - **inst/hex/hexSticker.Rmd**: Template for creating [hex stickers](https://github.com/GuangchuangYu/hexSticker). 
  - **.github/workflows/\*.yml**: [GitHub Actions](https://docs.github.com/en/actions/learn-github-actions/understanding-github-actions) workflow files that will automatically trigger code checks and pushing images to [DockerHub](https://hub-stage.docker.com/) every time you make a push to your GitHub repo (from [`rworkflows`](https://github.com/neurogenomics/rworkflows)).
  - **inst/CITATION** : Allows users of your package to call `citation("<packageName>")`. Also used to auto-populate the *README.Rmd*.  
  
To get started, simply click on the green **Use this template** button 
at the top right of the `templateR` repo. 

### GitHub Secrets  

To use certain features of `rworkflows`, you may need to set up one or more [GitHub Secrets](https://docs.github.com/en/actions/security-guides/encrypted-secrets):  

- `PAT_GITHUB` [Optional]: Can grant access to private repos on GitHub
  Actions. You can generate your very own Personal Authentication Token
  with `usethis::create_github_token()`. See the [GitHub
  docs](https://docs.github.com/en/authentication/keeping-your-account-and-data-secure/creating-a-personal-access-token)
  for details.  
- `DOCKER_TOKEN` [Optional]: Allows GitHub Actions to push to a
  [DockerHub](https://hub.docker.com) account.
  
### GitHub Pages

The [GitHub Actions](https://docs.github.com/en/actions/learn-github-actions/understanding-github-actions) workflows included in this template will automatically create a documentation website for your package via [GitHub Pages](https://pages.github.com/).  

After the **`rworkflows` action** has successfully run on Ubuntu for the 
first time, a new branch will appear in your repo called "gh-pages".   

**\<---⬆️⬆️⬆️(End of section that can be deleted after forking the template)⬆️⬆️⬆️---\>** 

## ``r pkg``: `r gsub("\n","",title)`

### `r gsub("\n","",description)`
 
If you use ``r pkg``, please cite: 

<!-- Modify this by editing the file: inst/CITATION  -->
> `r utils::citation(pkg)$textVersion`

## Installation 

```R
if(!require("remotes")) install.packages("remotes")

remotes::install_github("`r paste(owner,repo,sep='/')`")
library(`r pkg`)
```
## Documentation 

### [Website](https://`r owner`.github.io/`r repo`) 
### [Getting started](https://`r owner`.github.io/`r repo`/articles/`r pkg`) 

<hr>

## Session Info

<details>
```{r}
utils::sessionInfo()
```
</details>

