---
title: "hexSticker"
date: "<h4>Updated: <i>`r format( Sys.Date(), '%b-%d-%Y')`</i></h4>"
output:
  rmarkdown::html_document
vignette: >
  %\VignetteIndexEntry{hexSticker}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, echo=FALSE, include=TRUE}
#### Install deps ####
for(p in c("hexSticker","dplyr","here")){
    if(!require(p,character.only = TRUE)) install.packages(p)     
}
#### Get package metadata deps ####
pkg <- read.dcf(here::here("DESCRIPTION"), fields = "Package")[1]
description <- read.dcf(here::here("DESCRIPTION"), fields = "Description")[1]
```

# Create hex sticker

Hex stickers are a great way to give your R package its very own logo. 
See [here for some examples](http://hexb.in/) from other packages. 

Here are some R packages that you may find helpful for making hex stickers:

## [`hexSticker`](https://github.com/GuangchuangYu/hexSticker)  
Helper functions for creating reproducible hexagon sticker purely in R.

## [`ggimage`](https://github.com/GuangchuangYu/ggimage) 
Supports image files and graphic objects to be visualized in `ggplot2` graphic system.

## [`ggpattern`](https://coolbutuseless.github.io/package/ggpattern/)
Custom `ggplot2` geoms which support filled areas with geometric and image-based patterns.

## [`magick`](https://cran.r-project.org/web/packages/magick/vignettes/intro.html)
Advanced Image-Processing in R.

## [`aRtsy`](https://github.com/koenderks/aRtsy)
R package for making generative art using `ggplot2`.

## [`threed`](https://github.com/coolbutuseless/threed)
Three-Dimensional Object Transformations.

## Create file path

Create file path to save hex sticker to.

```{r}
filename <- here::here("inst","hex","hex.png")
dir.create(dirname(filename), showWarnings = FALSE, recursive = TRUE)
```


## Using `hexSticker::sticker`
## Create cube hex

```{r}
#### Install dep ####
if(!require("threed")){
    remotes::install_github("coolbutuseless/threed")
}
#### Change view perspective ####
camera_to_world <- threed::look_at_matrix(eye = c(4, 4, 4), 
                                          at = c(0, 0, 0)) 
obj <- threed::mesh3dobj$cube |>
    threed::rotate_by(angle = 0, v = c(0, 1, 0)) |>
    threed::transform_by(threed::invert_matrix(camera_to_world)) |>
    threed::orthographic_projection()
    
#### Make ggplot ####
ggcube  <- ggplot2::ggplot(as.data.frame(obj)) + 
    ggplot2::geom_polygon(
      ggplot2::aes(x = x, y = y, 
                   group = zorder, 
                   linetype = hidden,  size = hidden,
                   fill = 0.5 * fnx + fny), 
      color = ggplot2::alpha("black",.25),
      size = .25, 
      # alpha=1,
      show.legend = FALSE) +
    ggplot2::scale_linetype_manual(values = c('TRUE' = "FF", 'FALSE' = 'solid')) +
    # ggplot2::scale_size_manual(values = c('TRUE' = 0.2, 'FALSE' = 0.5)) +
    # ggplot2::scale_fill_viridis_c(option = "plasma") + 
    ggplot2::scale_fill_gradientn(
        colors = ggplot2::alpha(rev(RColorBrewer::brewer.pal(9, "PuBuGn")), 
                                alpha = .5)) + 
    ggplot2::theme_void() + 
    ggplot2::coord_equal()
ggcube
```

## Make sticker 

```{r}    
s_size = 2
stick <- hexSticker::sticker( 
  subplot = ggcube,
  #### Package name ####
  package = pkg, p_size=20, p_y = 1.48, p_color = ggplot2::alpha("black",.5),
  #### Subplot #####
  s_x=1, s_y=1,  s_height = s_size, s_width = s_size,
  #### Fill & border ####
  h_fill = "white", h_color = ggplot2::alpha("black",.25),
  #### Spotlight ####
  spotlight = TRUE, l_alpha = .3, l_width = 10, l_x = .5, l_y = .75,
  #### File output ####
  dpi = 300, filename = filename)
print(stick)
```


## Using `hexSticker::geom_hexagon`

```{r} 
gghex <- 
    hexSticker::ggplot() +
    hexSticker::geom_hexagon(fill = ggplot2::alpha("black",.75), 
                             color = ggplot2::alpha("white",.5)) +
    hexSticker::geom_pkgname(package = pkg, 
                             size=20, 
                             color = ggplot2::alpha("white",.5)) +
    hexSticker::theme_sticker()  

hexSticker::save_sticker(filename = filename,
                         sticker = gghex)
print(gghex)
```


# Session Info 

<details> 

```{r Session Info}
utils::sessionInfo()
```

</details>  
